%-------------------------
% Resume in Latex
% Author : Yao-Chung Chang
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\baselinestretch}{1.3} 

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Yao-Chung Chang}} & Email : {yaochung9744@gmail.com}\\
  &Mobile : (+886)903393682 \\
  &Address : {10F.-1, No.72, Sec. 2, Xinyi Rd.}\\
  &{,Da’an Dist., Taipei City 106, Taiwan}
  
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Taiwan University}{Taipei, Taiwan}
      {Computer Science Major; required courses GPA(last two years): 3.6}
      {Aug. 2015 -- Jun. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dynasafe Technologies, Inc.}{Neihu, Taipei}
      {Network Engineer Intern}{Jan 2018 -- Mar 2018}
      \resumeItemListStart
        \resumeItem{re-install the operating system of BIG-IP}
          {F5's BIG-IP is a family of products covering software and hardware designed around application availability, access control, and security solutions.}
        \resumeItem{Building LAMP environment}
          {LAMP is the names of original four open-source components: the GNU/Linux operating system, the Apache HTTP Server, the MySQL relational database management system (RDBMS), and the PHP programming language.}
      \resumeItemListEnd

    \resumeSubheading
      {Courses}{National Taiwan University, Taipei}
      {Required and elective courses}{Aug. 2015 -- Sep. 2018}
      \resumeItemListStart
        \resumeItem{Data Structure}
          {Understanding the principle and the complexity of common data structures and use them to complete some projects in C++ language.}
        \resumeItem{Algorithm design and analyze}
          {Learning how to design the efficient algorithms to the problems and proving its correctness and complexity.}
        \resumeItem{System programming in the unix environment}
          {Knowing how the program works and learning how to use API in Unix system such as FILE I/O, signal, thread, etc.}
        \resumeItem{Computer network}
          {Unstanding the concept of five layers Internet protocols and using sockets to simulate TCP Sliding Window algorithm in python.}
        \resumeItem{Introduction to Cryptography}
          {Understanding the principle of symmetric-key algorithm(AES, DES), asymmetric-key algorithm(RSA) and some abstract algebra behind them.}
        \resumeItem{machine learning}
          {Understanding the principle of some machine learning algorithms and the distributions and the properties of data.}
      \resumeItemListEnd
      
     \resumeSubheading
      {Skills}{Computer related}
      {self taught and learn from school}{Aug. 2015 -- Jun. 2019}
      \resumeItemListStart
        \resumeItem{Programming languages}
          {C, C++, python, php(basic), html/css(use bootstrap), shell script(basic)}
         \resumeItem{Mathematic}
          {Calculus, Linear Algebra, Probability, Discrete mathematics}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Volunteer experience}
  \resumeSubHeadingListStart
    \resumeSubItem{NTU Tutoring Club Member, fall 2017}
      {Making senior high school students clear on the math problems and helping them finish their homework.}
    \resumeSubItem{Formosa Plastic Group Museum Volunteer Guide}
      {Assisting visitors from different locations and ensure the highest level of customer service.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
